\papertitle

### 2013-02-05 manuscript.tex
fixed bibliography, other text things

Our system combines both the sensing of the H$^2$Bird and the execution of the
desired headings to steer the robot towards the goal. The sensing is performed
on the ground station using frame differencing and a particle filter. The
H$^2$Bird steers to the heading directed by the ground station using a
quaternion-based PID controller.

@@

In this section, we describe the models that we developed to simulate the
behaviors of the ornithopter and the ground station. We use these models to
determine the set of initial conditions that are most likely to result in
successful window traversal.

@@

We approximate the yaw dynamics of the ornithopter with a one-dimensional model to 
limit complexity, and because it matches our physical implementation. The H$^2$Bird 
uses an on-board PID controller to follow a particular heading sent by the ground 
station, and the yaw dynamics are largely decoupled from the rest of the fight dynamics, 
so our one-dimensional model is a good representation of the yaw motion:
\begin{equation}
\label{eq:plain_model}
\begin{aligned}
& H(s) = \frac{K}{1 + Rs}
& \text{where }H(s) = \frac{\theta(s)}{u(s)}
\end{aligned}
\end{equation}
We choose the reference heading angle as the input to the model, $u(s)$, and
model the dynamics of vehicle and on-board PID controller as one system, whose
output is the physical heading angle of the H$^2$Bird, $\theta(s)$. To model the translational position of
the ornithopter, we use a form of Dubin's car model~\cite{lavalle:planning}:
\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation} 
In the car model, $\phi_{max}$ is the maximum steering angle and $u_{s}$ is
the forward speed. We modify this model to treat the angular position $\theta$
as an input rather than a state. The overall motion of the system can be
modeled as shown in Equation~\ref{eq:dubin_car}, where $\theta$ is the
time-domain output of Equation~\ref{eq:plain_model}, $\theta(t)$.

@@

Our model of the ground station includes models for both the camera and the
pose estimation computation. The camera model contains both a latency, which 
is in series with the path between the ``Camera'' and 
``Ornithopter Dynamics'' blocks in Figure~\ref{fig:block_diagram}, and a 
model of the camera's viewing angle constraints.

We model the viewing angle of the camera as a pixel map from one edge of a 
63$^{\circ}$ viewing triangle to the other. The camera has an image width of 
640 pixels. We calculate the desired heading angle in degrees, for a given 
distance from the camera:
\begin{equation} 
\label{eq:desired_heading} 
\text{Desired heading} = \frac{640\,\text{px}}{2d\tan{\frac{63^{\circ}}{2}}}{\times\frac{63^{\circ}}{640\,\text{px}}\times x}
\end{equation}
where $d$ is the distance between the ornithopter and the camera, and $x$ is 
the horizontal position of the robot relative to the center of the window in 
meters. This relation reflects the fact that the pose estimation algorithm 
does not determine the depth of the robot, which can be problematic for 
control algorithms. For example, if the ornithopter remains at a constant 
horizontal distance from the window, but moves closer and closer to the 
camera, the ground station's directed heading steadily increases, even 
though the robot has not actually moved farther from the window. These 
problems are most severe in areas close to the camera.

We experienced latency during experiementation in estimating the pose of the
ornithopter on the ground station. Referring to
Figure~\ref{fig:block_diagram}, there were delays in the pose estimation block
while updating the particle filter, in the PID controller block when
calculating the new reference attitude, and in the transmission of the desired
heading from the external controller to the controller on the robot via radio.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments, Results, and Performance}
\label{sec:performance}
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal, using both analytical and empirical methods. We then 
conduct experiments to validate this model.

@@

We measured a camera capture latency of 40 ms, pose estimation computation 
latency of 12.5 ms, and radio latency of 25 ms.
%----------------------------------------------------------------------------%
\subsection{Model Verification}

@@

In Figure ~\ref{fig:feasible_set}, 
the blue lines represent the camera viewing triangle, the black line represents the window, and the black 
dot represents the camera. For the initial conditions, we used a uniform
grid of 5 cm increments within the camera viewing region, and an initial
angular heading perpendicular to the window plane. A success, or feasible 
initial condition, consists of a path that intersects the window at some 
point and does not leave the camera viewing triangle, and is indicated in 
green. The geometrically infeasible region is computed using the minimum 
turning radius and the geometry of the camera's field-of-view and is 
indicated in blue. The region in red is not geometrically feasible, but is 
infeasible as a result of the cooperative control simulation dynamics.

We conducted a Monte Carlo simulation to determine the probability of
successful window navigation for a given point within the testing area. Using
this information we can make assumptions about ideal starting positions for
cooperative control. For each point within a 10 cm grid within the camera
viewing triangle, we simulated 40 trials using an initial heading randomly
sampled from a uniform distribution between -90$^{\circ}$ and 90$^{\circ}$,
with the 0$^{\circ}$ heading perpendicular to the window.
Figure~\ref{fig:heat_map} depicts the results of the Monte Carlo simulation.

@@

Each trial included the following steps (see Figure~\ref{fig:pf_screencap}):
\begin{spaced_description}{\textbf{(4-6)}}
\item[\textbf{(1,2)}] We identify the window to the ground station by dragging a bounding 
box over it using a mouse. 
\item[\textbf{(3)}] We release H$^2$Bird by hand, in view of the camera at the desired 
starting grid point.
\item[\textbf{(4-6)}] The H$^2$Bird attempts to fly through the window, with remote 
guidance from the ground station.
\end{spaced_description}

@@

Conducting the experimental trials as described in 
Section~\ref{sec:experiments_verification}, we achieved a success rate of 
80\% for initial conditions in the middle of the testing space and in front 
of the camera. As we moved towards the edges of the feasible region in 
Figure~\ref{fig:flight_paths}, the success rate diminished to 50\%.

The lower success rate on the edges of the camera frame can be explained by 
several factors. On the edges of the viewing triangle, the yaw control 
inputs are large in magnitude, although this is not necessary in all cases. 
Since the control algorithm we are using has no notion of depth, it applies 
the same control input whether the ornithopter is close to the camera, where 
small changes in heading are adequate, or far away from the camera, where 
large changes in heading are necessary. Due to this phenomenon, the 
controller often over or under-compensates in certain regions, depending 
upon the PID tuning and the distance from the camera. Tracking noise can 
also cause passage negotiation to fail. Variations in the H$^2$Bird hand 
launch can cause the system to respond differently for similar initial 
conditions. In addition, we changed the H$^2$Bird battery approximately every 5 
tests, adding more variation to the H$^2$Bird performance by affecting the 
motor power output.

The results of our experimental trials verify the results of the Monte Carlo
simulation of our model. The trials that we conducted in
Figure~\ref{fig:flight_paths_feasible} correspond to the circled region in
Figure~\ref{fig:heat_map}. The 80\% success rate that we measured in the
experiments corroborates our calculated probability of success of
approximately 80\%. Additionally, the diminished success rate of 50\% near the
edges of the viewing triangle that we determined through experimentation
supports the reduced probability of success calculated by the simulation.

Our experimental data validates Figure~\ref{fig:feasible_set}, as there are 
no successes within the geometrically infeasible region. There are few 
successes near the boundary of the infeasible region determined in 
simulation. While there are successes along the boundary of the camera 
viewing triangle, there are also many failures. We further explore this 
behavior using a Monte Carlo simulation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
We have demonstrated cooperative guidance of a 13 gram flapping-wing MAV with
a lightweight base station in hardware. In addition, we developed a model of
the cooperative system using system identification methods on the individual
system capabilities, and composing it with known system interactions. The
corroboration between our simulated and experimental results shows that our
simplified modeling approach is useful for predicting the performance of
cooperative systems at low computational cost. Our model could also be used to
determine when to begin control with high probability of success, even though
we lack information about the complete pose of the MAV.

>>>>

Our system combines both the sensing of the H$^2$Bird and the execution of the
desired headings to steer the robot towards the goal. The sensing is performed
on the ground station using frame differencing and a particle filter. The
H$^2$Bird steers to the heading directed by the ground station using a
quaternion-based proportional-integral-derivative controller.

@@

We developed models using system identification concepts to simulate the
behaviors of the H$^2$Bird and the ground station. We use these models to
determine the set of initial conditions that are most likely to result in
successful window traversal.

@@

We approximate the yaw dynamics of the ornithopter with a one-dimensional model to 
limit complexity, and because it matches our physical implementation. The H$^2$Bird 
uses an on-board PID controller to follow a particular heading sent by the ground 
station, and the yaw dynamics are largely decoupled from the rest of the fight dynamics, 
so our one-dimensional model is a good representation of the yaw motion:
\begin{equation}
\label{eq:plain_model}
\begin{aligned}
& H(s) = \frac{K}{1 + Rs}
& \text{where }H(s) = \frac{\theta(s)}{u(s)}
\end{aligned}
\end{equation}
We choose the reference heading angle as the input, $u(s)$, to the model, and
model the dynamics of vehicle and on-board PID controller as one system, whose
output, $\theta(s)$, is the physical heading angle of the H$^2$Bird. To model the translational position of
the ornithopter, we use a form of Dubin's car model~\cite{lavalle:planning}:
\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation} 
In the car model, $\phi_{max}$ is the maximum steering angle and $u_{s}$ is
the forward speed. We modify this model to treat the angular position $\theta$
as an input rather than a state. The overall motion of the system can be
modeled as shown in Equation~\ref{eq:dubin_car}, where $\theta$ is the
time-domain output of Equation~\ref{eq:plain_model}, $\theta(t)$.

@@

Our model of the ground station includes models for both the camera and the
pose estimation computation. Both models contain latencies, which we
identified in several locations in the block diagram in
Figure~\ref{fig:block_diagram}. The camera model experiences a delay in series
with the path between the ``Camera'' and ``Ornithopter Dynamics'' blocks. The
pose estimation algorithm experiences latency in the pose estimation block
when updating the particle filter, and during the transmission of the desired
heading from the external PID controller to the internal PID controller on
the robot, via radio.

In addition to the latencies in the system, we model the viewing angle of the
camera as a pixel map from one edge of a 63$^{\circ}$ viewing triangle to the
other. The camera has an image width of 640 pixels. We calculate the desired
heading angle in degrees, for a given distance from the camera:
\begin{equation} 
\label{eq:desired_heading} 
\text{Desired heading} = \frac{640\,\text{px}}{2d\tan{\frac{63^{\circ}}{2}}}{\times\frac{63^{\circ}}{640\,\text{px}}\times x}
\end{equation}
where $d$ is the distance between the ornithopter and the camera, and $x$ is 
the horizontal position of the robot relative to the center of the window in 
meters. This relation reflects the fact that the pose estimation algorithm 
does not determine the depth of the robot, which can be problematic for 
control algorithms. For example, if the ornithopter remains at a constant 
horizontal distance from the window, but moves closer and closer to the 
camera, the ground station's directed heading steadily increases, even 
though the robot has not actually moved farther from the window. These 
problems are most severe in areas close to the camera.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Results}
\label{sec:performance}
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal, using both analytical and empirical methods. We then 
conduct experiments to validate this model.

@@

We measured a camera capture latency of 40 ms, pose estimation computation 
latency of 12.5 ms, and radio transmission latency of 25 ms.
%----------------------------------------------------------------------------%
\subsection{Model Verification}

@@

In Figure ~\ref{fig:feasible_set}, 
the blue lines represent the camera viewing triangle, the black line represents the window, and the black 
dot represents the camera. For the initial conditions, we used a uniform
grid of 5 cm increments within the camera viewing region, and an initial
angular heading perpendicular to the window plane. A success, or feasible 
initial condition, consists of a path that intersects the window at some 
point and does not leave the camera viewing triangle, and is indicated in 
green. The geometrically infeasible region is computed using the minimum 
turning radius and the geometry of the camera's field-of-view, and is 
indicated in blue. The region in red is geometrically feasible, but is 
infeasible as a result of the cooperative control simulation dynamics.

We conducted a Monte Carlo simulation to determine the probability of
successful window navigation for a given point within the testing area. Using
this information we can make assumptions about ideal starting positions for
cooperative control. For each point in a 10 cm grid within the camera
viewing triangle, we simulated 40 trials using an initial heading randomly
sampled from a uniform distribution between -90$^{\circ}$ and 90$^{\circ}$,
with the 0$^{\circ}$ heading perpendicular to the window.
Figure~\ref{fig:heat_map} depicts the results of the Monte Carlo simulation.

@@

Each trial included the following steps (see Figure~\ref{fig:pf_screencap}):
\begin{spaced_description}{\textbf{(4-6)}}
\item[\textbf{(1,2)}] We identify the window to the ground station by dragging a bounding 
box over it using a mouse. 
\item[\textbf{(3)}] We release the H$^2$Bird by hand, in view of the camera at the desired 
starting grid point.
\item[\textbf{(4-6)}] The H$^2$Bird attempts to fly through the window, with remote 
guidance from the ground station.
\end{spaced_description}

@@

As a result of the experimental trials, we achieved a success rate of 
80\% for initial conditions in the middle of the testing space and in front 
of the camera. As we moved towards the edges of the feasible region in 
Figure~\ref{fig:flight_paths}, the success rate diminished to 50\%.

The lower success rate on the edges of the camera frame can be explained by
several factors. On the edges of the viewing triangle, the yaw control inputs
are large in magnitude, although this is not necessary in all cases. Since the
control algorithm we are using has no notion of depth, it applies the same
control input whether the ornithopter is close to the camera, where small
changes in heading are adequate, or far away from the camera, where large
changes in heading are necessary. Due to this phenomenon, the controller often
over or under-compensates in certain regions, depending upon the PID tuning
and the distance from the camera. Tracking noise and variations in the
H$^2$Bird hand launch can cause the system to respond differently for similar
initial conditions, or to fail completely. In addition, we changed the
H$^2$Bird battery approximately every 5 tests, adding more variation to the
H$^2$Bird performance by affecting the motor power output.

The results of our experimental trials verify the results of the Monte Carlo
simulation of our model. The trials that we conducted in
Figure~\ref{fig:flight_paths_feasible} correspond to the circled region in
Figure~\ref{fig:heat_map}. The 80\% success rate that we measured in the
experiments corroborates our calculated probability of success of
approximately 80\%, demonstrated by the Monte Carlo simulation. Additionally,
the diminished success rate of 50\% near the edges of the viewing triangle
that we determined through experimentation supports the reduced probability of
success calculated by the simulation.

Our experimental data validates Figure~\ref{fig:feasible_set}, as there are 
no successes within the geometrically infeasible region. There are few 
successes near the boundary of the infeasible region determined in 
simulation. While there are successes along the boundary of the camera 
viewing triangle, there are also many failures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
We have demonstrated cooperative guidance of a 13 gram flapping-wing MAV with
a lightweight base station. In addition, we developed a model of
the cooperative system using system identification methods on the individual
system capabilities, and composing it with known system interactions. The
corroboration between our simulated and experimental results shows that our
simplified modeling approach is useful for predicting the performance of
cooperative systems at low computational cost. Our model could also be used to
determine when to begin control with high probability of success, even though
we lack information about the complete pose of the MAV.
